Ice-shelf ocean boundary layer dynamics from large-eddy simulations

### 2021-07-12 main.tex
Updates from Overleaf

% Description of time evolution
Melt rates decline over the course of the simulations (Figure \ref{fig:timeseries}), preventing the identification of steady-state melt rates for most runs. This decline is in response to the concomitant increase in stratification during the course of the simulations, which decreases vertical heat fluxes by reducing vertical turbulent fluctuations. We do not continue our simulations beyond 4 inertial periods in the hope of reaching steady-state conditions because the increase in stratification reduces the turbulent length scales and necessitates higher model resolution than we have used here. Our simulations generally show resolved turbulent fluxes exceeding the subgrid turbulent fluxes, but over the last inertial period the subgrid turbulent fluxes dominate within several meters of the ice base where the stratification is strongest (Figure S1).

>>>>

% Description of time evolution
Melt rates decline over the course of the simulations (Figure \ref{fig:timeseries}), preventing the identification of steady-state melt rates for most runs. This decline is in response to the concomitant increase in stratification during the course of the simulations, which decreases vertical heat fluxes by reducing vertical turbulent fluctuations. We do not continue our simulations beyond 4 inertial periods in the hope of reaching steady-state conditions because the increase in stratification reduces the turbulent length scales and necessitates higher model resolution than we have used here. Our simulations generally show resolved turbulent fluxes exceeding subgrid turbulent fluxes, but subgrid turbulent fluxes dominate within several meters of the ice base where the stratification is strongest (Figure S1).
